Local PCA Shows How Population Structure Differs Along the Genome

### 2016-04-12 writeup/local_pca_paper.tex
removed some comments

\begin{equation}
V_{1}=\sqrt{\frac{\lambda _{1i}}{\lambda _{1i}+\lambda _{2i}}}PC1_{i} \qquad
V_{2}=\sqrt{\frac{\lambda _{2i}}{\lambda _{1i}+\lambda _{2i}}}PC2_{i} \qquad
U_{1}=\sqrt{\frac{\lambda _{1j}}{\lambda _{1j}+\lambda _{2j}}}PC1_{j} \qquad
U_{2}=\sqrt{\frac{\lambda _{2j}}{\lambda _{1j}+\lambda _{2j}}}PC2_{j}
\end{equation}

@@

\begin{figure}
    \begin{center}
       \includegraphics[width=0.9\textwidth]{Fig1_Together_MDS_plot_Chr2L_final_abline}
    \end{center}
    \caption{
         Variation in structure for windows on chromosome arm Chr2L. 
         Each represents a window: (a) shows the MDS visualization of relationships between windows. 
         (b) and (c) show the position (midpoint) of each window against the first and second MDS coordinates, respectively. 
         Colors are consistent for (a) (b) and (c).
         Vertical black lines show the breakpoints of known polymorphic inversions In(2L)t.
         \plr{(I think it's a bit confusing having both MDS1D and MDS2D: can we instead of MDS1D on the right, just plot the first coordinate of MDS2D?  And, somehow make the colors agree between the two figures? (not sure how to do this)}
         \label{fig:mds_chr2L}
    }
\end{figure}

@@

\plr{Use figure labels, like ``Figure {\textbackslash}ref\{fig:mds{\textunderscore}chr2L\}'' instead of ``Figure 1''.}

>>>>

\begin{equation}
    \begin{aligned}
        V_{1}&=\sqrt{\frac{\lambda _{1i}}{\lambda _{1i}+\lambda _{2i}}}PC1_{i} \qquad
        V_{2}&=\sqrt{\frac{\lambda _{2i}}{\lambda _{1i}+\lambda _{2i}}}PC2_{i} \\
        U_{1}&=\sqrt{\frac{\lambda _{1j}}{\lambda _{1j}+\lambda _{2j}}}PC1_{j} \qquad
        U_{2}&=\sqrt{\frac{\lambda _{2j}}{\lambda _{1j}+\lambda _{2j}}}PC2_{j}
    \end{aligned}
\end{equation}

@@

\begin{figure}
    \begin{center}
       \includegraphics[width=0.9\textwidth]{Fig1_Together_MDS_plot_Chr2L_final_abline}
    \end{center}
    \caption{
         Variation in structure for windows on chromosome arm Chr2L. 
         Each represents a window: (a) shows the MDS visualization of relationships between windows. 
         (b) and (c) show the position (midpoint) of each window against the first and second MDS coordinates, respectively. 
         Colors are consistent for (a) (b) and (c).
         Vertical black lines show the breakpoints of known polymorphic inversions In(2L)t.
         \label{fig:mds_chr2L}
    }
\end{figure}

@@
